\pagenumbering{arabic}
\chapter{INTRODUCTION}
\section{Background}
The stock market is a crucial part of the global economy, where people and businesses invest to grow their wealth. However, it can be unpredictable and fast-moving, making it difficult for investors to keep up with changes and make the right decisions at the right time. Monitoring market trends, predicting price changes, and identifying the best opportunities require a lot of effort and expertise. By using advanced algorithms, technology can simplify these tasks, helping investors track and understand market patterns more easily and alerting the users when to invest and sell the stocks will help the users to connect with market adequately.



 \section{Problem Statement}
 While there are tools available to analyze the stock market, many of them have limitations. They often lack real-time updates, fail to provide personalized notifications, and do not predict future price movements effectively. These issues make it harder for users to make timely and well-informed decisions.The main problem in predicting share market is that the
share market is a chaos system. There are many variables
that could affect the share market directly or indirectly.
There are no significant relations between the variables and
the price. We cannot draw any mathematical relation
among the variables. There are no laws of predicting the
share price using these variables.
 This gap highlights the necessity for a comprehensive, user-centric platform that not only tracks stock market activity but also empowers users with actionable insights and timely alerts.


\section{Motivation}
The motivation for this project stems from the need to create a comprehensive tool that empowers users by providing real-time market data, customized notifications, and predictive analytics. This ensures that users can make informed choices and achieve their investment goals with greater ease.

\section{Objectives of the Study}

The primary objectives of this program are:
  \begin{enumerate}

\item To estimate future price movements using LSTM algorithm.

\item To alert users when their target prices align with projections.

\item To streamline market tracking by delivering real-time information and personalized insights, enabling users to make smarter investment decisions.
\item To study the risks and challenges of AI in stock market prediction.
  \end{enumerate}



    




