\chapter{LITERATURE REVIEW}
\section{ Introduction}
Stock market tracking and prediction tools have become essential for investors seeking to make informed decisions in a fast-moving and unpredictable market. Numerous platforms exist that claim to help users predict price movements and track trends, but each has its own strengths and weaknesses. This section reviews the existing tools and highlights their limitations, explaining how StockHawk addresses these gaps.

\subsection {Traditional Stock Market Tracking Tools}

Traditional stock market tracking tools, such as Yahoo Finance, Google Finance, and Bloomberg, provide basic functionalities like real-time stock price tracking, historical data analysis, and financial news. These platforms typically focus on displaying data and offering some basic charting features.

% \textbf{Limitations:}
% While these tools are useful for observing current market data, they lack advanced prediction capabilities. They do not provide personalized alerts or predictive analytics that are tailored to individual user goals. Additionally, they focus mainly on historical data and do not offer real-time, actionable insights based on current market conditions.

% \textbf{How StockHawk Addresses the Gap:}
% StockHawk goes beyond traditional tracking by offering personalized, real-time alerts when target prices align with predicted price movements. The platform’s advanced algorithms help estimate future price trends, making it a powerful tool for proactive decision-making. Unlike traditional tools that focus primarily on price history, StockHawk enables users to anticipate market shifts before they occur.


\subsection {Machine Learning and AI-Based Tools}

More advanced platforms like TrendSpider and Kavout use machine learning and AI algorithms to predict future stock prices. These platforms attempt to automate the analysis of stock trends by applying deep learning models to large datasets.

% \textbf{Limitations:}
% While machine learning-based tools are capable of making predictions, they can be opaque in terms of how decisions are made. Many AI-based platforms lack transparency, making it difficult for users to understand the rationale behind predictions. Additionally, these systems can be computationally expensive, and their results may not always be accessible to non-expert users.

% \textbf{How StockHawk Addresses the Gap:}
% StockHawk integrates advanced algorithms for price prediction in a user-friendly interface, making it more accessible to a wider range of users, from beginners to experts. The platform is designed to offer transparency and clarity in its predictions, with clear explanations of the reasoning behind the alerts and projections. Moreover, StockHawk focuses on providing personalized insights and real-time updates, ensuring users receive relevant information tailored to their investment goals.

% \section{ Limitations of Existing Tools and StockHawk’s Advantages}

% The major \textbf{limitations }of current stock tracking and prediction tools are:

% A lack of personalized alerts and real-time, actionable insights.
% Limited predictive capabilities, often focusing only on past performance.
% A steep learning curve for tools requiring technical expertise.
% Insufficient integration of real-time data with forecasting algorithms.

% \textbf{StockHawk addresses these issues by:}

% Offering personalized notifications and alerts based on user-defined target prices and projections.
% Using advanced algorithms to estimate future price movements, providing users with foresight to make informed decisions.
% Simplifying the tracking and analysis process, making it accessible even to beginners while still powerful for advanced users.
% Delivering real-time information and insights to help users stay updated with minimal delay, allowing them to act quickly when opportunities arise.
\section{Challenges of AI in Stock Price Prediction}
\begin{enumerate}
    \item \textbf{The complexity of the stock market and unpredictable external factors}\\ The stock market is a complex system that is impacted by a wide range of factors, including economic data,
political developments, and even calamities. AI can analyze a lot of data and spot trends that humans would
overlook. However, it can't always foresee unforeseen circumstances that have a significant impact on the
market.
    \item \textbf{Risk of overreliance on AI predictions}\\
    Another issue is the potential for overconfidence in AI predictions. Owners should keep in mind that AI is
not flawless, even if it can provide them with helpful information and assist them in making better financial
decisions. Never rely solely on one source of information while making financial decisions, and always
consider multiple sources of data.
\item \textbf{Need for continuous human monitoring and intervention}
\\
Finally, people must keep an eye on things and intervene as necessary. Many aspects of stock market
research can be handled by AI, but humans must still monitor the system and intervene as needed. This can
make it more likely that the AI's predictions will be accurate and that any errors will be swiftly identified
and fixed.
\end{enumerate}
    