\chapter{RELATED THEORY}
\section{Related Theory:}
Stock market analysis relies on a combination of theoretical frameworks and advanced computational techniques. StockHawk incorporates these principles to provide users with a comprehensive tool for monitoring and predicting stock market movements. Below is a discussion of foundational theories in stock market analysis and how they relate to StockHawk’s features and objectives.

\textbf{1. Time-Series Forecasting}

Time-series forecasting is a statistical technique used to analyze and predict future values based on historical data. In stock market analysis, it helps identify trends, seasonality, and cyclic patterns in stock prices.

\textbf{Application in StockHawk:}

StockHawk uses time-series forecasting to estimate future price movements. By leveraging historical stock data and applying algorithms such as ), LSTM - exponential smoothing, and neural networks, the platform generates accurate predictions of future price trends. These predictions empower users to anticipate changes in the market and make informed decisions about buying, selling, or holding their investments.

\textbf{ Objective Alignment:}

To estimate future price movements using advanced algorithms: StockHawk's forecasting capabilities enable users to plan their strategies based on data-driven insights.

\textbf{2. Pattern Recognition}

Pattern recognition involves identifying recurring structures or behaviors in data. In stock market analysis, it is used to detect trends, support and resistance levels, and technical indicators such as head-and-shoulders patterns or moving averages.

\textbf{Application in StockHawk:}

StockHawk integrates pattern recognition techniques to track stock market patterns effectively. Machine learning models and technical analysis tools help identify significant market signals, allowing users to understand the broader market dynamics and make timely decisions.

\textbf{Objective Alignment}:

To track stock market patterns effectively: By recognizing key patterns, StockHawk simplifies complex market data into actionable insights.

\textbf{3. Real-Time Data Processing and Alerts}

In today’s fast-paced markets, real-time information is crucial. Technologies like data streaming, API integration, and low-latency systems enable platforms to deliver updates almost instantly.

\textbf{
Application in StockHawk:}

StockHawk provides real-time data and personalized alerts. By continuously monitoring market conditions, it notifies users when their target prices match projections. This feature ensures that users never miss critical opportunities, enhancing their ability to act promptly.

\textbf{Objective Alignment:}

To alert users when their target prices align with projections: Real-time alerts are tailored to each user’s goals, keeping them informed and prepared to act.
To streamline market tracking by delivering real-time information and personalized insights: The platform’s ability to process and display real-time data ensures users can rely on up-to-date information for decision-making.

\textbf{4. Behavioral Finance and Decision-Making Support}

Behavioral finance examines the psychological influences on investors’ decisions, such as fear, greed, and overconfidence. Recognizing these biases helps design systems that guide users toward rational decision-making.

\textbf{Application in StockHawk:}

By offering clear, data-driven insights and removing the noise of irrelevant information, StockHawk supports users in making smarter investment choices. Personalized insights help users overcome emotional biases and focus on objective analysis.

\textbf{Objective Alignment:}

To streamline market tracking by delivering real-time information and personalized insights: StockHawk’s intuitive interface and insights reduce cognitive overload, making complex information more accessible and actionable.



